### 2025-09-23 paper/sec/introduction.tex
add conclusion.
Resolve figref.

We also consider \emph{trend} expressions, which comparative natural language phrases describing how a data
attribute evolves over time, such as \textfrag{training time growing from 67 to 106 seconds}. Such idioms are
mapped to higher-order functions like \kw{trendWord} which are parameterised on additional helper functions
such as \kw{growShrink} and \kw{betterWorse} (\figref{}) which map comparisons to appropriate natural language
phrases.

@@

Taken together, these categories cover a representative portion of the numerical reasoning idioms found in the
SciGen benchmark. However, some common linguistic forms are not covered in our analysis. We have yet to study
approximate quantitative terms like \textfrag{around 50\%} or \textfrag{roughly 100 instances}, nor
interval-based descriptions such as \textfrag{between 30 and 40\%} or \textfrag{within 5–10 seconds}. We have
no reason for thinking these will present specific difficulties, however. Other forms are likely to be more
challenging. So-called \emph{graded} modal adverbs~\citep{lassiter17} which modify adjectival comparatives
like ``better`` -- like \textfrag{slightly better} and \textfrag{significantly higher} -- especially when
combined with trends over time, as in \textfrag{steadily increasing} or \textfrag{sharply declining}, because
the interpretation of these qualifiers is quite subjective and contextual. Adverbial quantifiers like
\textfrag{generally} and \textfrag{usually} also present challenges because colloquial use (``most'' meaning
``greater than any other alternative proportion'' may differ from more formal uses (``most'' meaning a
majority, i.e.~greater than 50\% of cases). Extending coverage to these idioms would substantially deepen our
tool's ability to bridge natural language reporting with interpretation in terms of the underlying dataset. We
discuss this further in \secref{future-work}.

>>>>

We also consider \emph{trend} expressions, which comparative natural language phrases describing how a data
attribute evolves over time, such as \textfrag{training time growing from 67 to 106 seconds}. Such idioms are
mapped to higher-order functions like \kw{trendWord} which are parameterised on additional helper functions
such as \kw{growShrink} and \kw{betterWorse} (shown in \figref{fluid-scigen}) which map comparisons to
appropriate natural language phrases.

@@

Taken together, these categories cover a representative portion of the numerical reasoning idioms found in the
SciGen benchmark. However, some common linguistic forms are not covered in our analysis. We have yet to study
approximate quantitative terms like \textfrag{around 50\%} or \textfrag{roughly 100 instances}, nor
interval-based descriptions such as \textfrag{between 30 and 40\%} or \textfrag{within 5–10 seconds}. We have
no reason for thinking these will present specific difficulties, however. Other forms are likely to be more
challenging. So-called \emph{graded} modal adverbs~\citep{lassiter17} which modify adjectival comparatives
like ``better`` -- like \textfrag{slightly better} and \textfrag{significantly higher} -- especially when
combined with trends over time, as in \textfrag{steadily increasing} or \textfrag{sharply declining}, because
the interpretation of these qualifiers is quite subjective and contextual. Adverbial quantifiers like
\textfrag{generally} and \textfrag{usually} also present challenges because colloquial use (``most'' meaning
``greater than any other alternative proportion'' may differ from more formal uses (``most'' meaning a
majority, i.e.~greater than 50\% of cases). Extending coverage to these idioms would substantially deepen our
tool's ability to bridge natural language reporting with interpretation in terms of the underlying dataset. We
discuss this further in \secref{conclusion:future-work}.
